Re-finding to support a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/ontological_realms.tex
ontological_realms.tex - Paragraph 2 #1 (modification based on the below comment)
Content: "By using OWL, we can exploit the OWL API for matching SSQ
ontologies that reference these realm ontologies."

Comment: OWL is just thrown in without any prior reference (that I
saw), we need to introduce what OWL is so we have a better context for
this (one of the reasons why we are using OWL).

To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass} and \textit{subclass} relationships built using the DBPedia properties \textit{broader} and \textit{narrower}. By using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.

@@

Once the semantic hierarchy is created, the next step is to create
training data for the system. The task is then to grab the pages,
build a corpus relating to a given category, and then compile the
information in a meaningful way. The overall goal is to grab enough
information to properly characterize a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia/Wikipedia heterarchy
contains a set of information pages, P, corresponding to the concepts shared by the category. Since the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket \cite{Friedman97bayesiannetwork} to describe
a particular category. Our assumption is that a
node can be fully described by its ancestor, descendant, and spousal
nodes (parent node of subcategory not equal to the category). While
this does not completely solve the issue of a category residing in a
sparse area of the graph, the amount of information that can be
obtained per blanket is usually more helpful than per category.

>>>>

To support our process, we map DBPedia categories into classes in our realm ontology with the \textit{superclass} and \textit{subclass} relationships built using the DBPedia properties \textit{broader} and \textit{narrower}. This  semantic heterarchy can be easily represented using the OWL ontology and by using OWL, we can exploit the OWL API for matching SSQ ontologies that reference these realm ontologies.

@@

Once the semantic heterarchy is created, the next step is to create
training data for the system. The task is then to grab the pages,
build a corpus relating to a given category, and then compile the
information in a meaningful way. The overall goal is to grab enough
information to properly characterize a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia/Wikipedia heterarchy
contains a set of information pages, P, corresponding to the concepts shared by the category. Since the categorical structure is a directed acyclic graph \cite{Suchanek07yago:a}, we use of a Markov Blanket \cite{Friedman97bayesiannetwork} to describe
a particular category. Our assumption is that a
node can be fully described by its ancestor, descendant, and spousal
nodes (parent node of subcategory not equal to the category). While
this does not completely solve the issue of a category residing in a
sparse area of the graph, the amount of information that can be
obtained per blanket is usually more helpful than per category.
